\chapter*{Contributions}

\begin{itemize}
    
    \item Drews MS., Leonhardt A., Pirogova N., \textbf{Richter FG.}, Schuetzenberger A., Braun L., Serbe E., Borst, A. (2020). Dynamic Signal Compression for Robust Motion Vision in Flies. \textit{Current Biology} 30, 209-221.
    
    \begin{itemize}
        \item
        % \paragraph{Contributions}
        M.S.D., A.L., and A.B. jointly conceived the study. M.S.D. and A.L. designed all experiments. A.L. and L.B. conducted behavioral experiments. E.S. recorded electrophysiological responses. M.S.D., N.P., \textbf{F.G.R.}, and A.S. performed calcium imaging. A.L. designed and analyzed the convolutional model. M.S.D. and A.L. analyzed data, performed modelling, and wrote the manuscript. All authors participated in editing the manuscript.
    \end{itemize}
    
    \item \textbf{Richter FG.}, Fendl S., Haag J., Drews MS., Borst A. (2018). Glutamate Signaling in the Fly Visual System. \textit{iScience} 7, 85-95.
    
    \begin{itemize}
        \item
        % \paragraph{Contributions}
        \textbf{F.G.R.}, S.F., and A.B. conceived the study and designed the experiments. \textbf{F.G.R.} conducted and analyzed the imaging experiments for Mi9 and L1. S.F. performed and analyzed all stainings. J.H. performed and analyzed the LPi experiments. M.S.D. performed data analysis and model fitting of the receptive fields. F.G.R. wrote the manuscript with the
help of all authors.
    \end{itemize}
    
    \item Arenz A., Drews MS., \textbf{Richter FG.}, Ammer G., Borst A. (2017). The Temporal Tuning of the \textit{Drosophila} Motion Detectors Is Determined by the Dynamics of Their Input Elements. \textit{Current Biology} 27, 929-944.
    
    \begin{itemize}
        \item
        % \paragraph{Contributions}
        A.A., M.S.D., and A.B. conceived the study and designed the experiments. A.A. conducted and analyzed the measurements of T4/T5 cell  responses. M.S.D.
        designed the projector-based stimulation arena and performed and analyzed the measurements of the OFF-pathway elements. \textbf{F.G.R.} performed and analyzed the experiments describing the ON-pathway neurons. G.A. performed and analyzed the patch-clamp recordings from lobula plate tangential cells. M.S.D. performed the computer simulations. A.A. wrote the manuscript with the help of all authors.
    \end{itemize}
    
    
    
\end{itemize}

\vspace{15mm}

  \begin{minipage}[t]{0.5\linewidth}
    \sign{Florian Richter}
    % \par 
    % Munich, Date
  \end{minipage}
  \begin{minipage}[t]{0.5\linewidth}
    \raggedright
    \sign{Sandra Fendl}
    \par
    Co-author
  \end{minipage}%
  
  \vspace{5mm}
  
    \begin{minipage}[t]{0.5\linewidth}
    \sign{Prof. Dr. Alexander Borst}
    \par 
    Supervisor
  \end{minipage}

\newpage