\chapter*{Curriculum vitae}

\section*{Education}

\begin{itemize}
    \item 2016--present: PhD student at Graduate School for Systemic Neurosciences (LMU Munich)/Max-Planck-Institute for Neurobiology, Germany; supervised by Alexander Borst
    
    \item 2015--2016: B.Sc in Biology at the Ludwigs-Maximilians Universität Munich, Germany
    
    \item 2011--2014: B.Sc in Biology at the Julius-Maximilians Universität in Würzburg, Germany
    
    \item 2011: Abitur at Gymnasium Marktbreit, Germany
\end{itemize}

\section*{Conferences \& Meetings}

\begin{itemize}
     \item 2018: Poster presentation at SFN Conference (San Diego, US)
     \item 2018: Poster presentation at FENS Conference (Berlin, Germany)
     \item 2017: Poster presentation at École de neuroscience (Paris, France)
     \item 2016: Poster presentation at FENS Conference (Copenhagen, Denmark)

\end{itemize}

\section*{Teaching}

\begin{itemize}
     \item Teaching assistant for \textit{Neurobiology Course} in 2014 (JMU Würzburg)
     \item Teaching assistant for \textit{Introduction to 2-photon imaging} in 2017 (MPI of Neurobiology)
\end{itemize}

\section*{Personal information}

\begin{itemize}
     \item Birthday: 15\textsuperscript{th} May 1990
     \item Nationality: German
     \item Languages: German (native), English (fluent), French (intermediate)
     \item Programming languages: Python (experienced), LaTeX (intermediate)
\end{itemize}

\section*{Publications}

\begin{itemize}

    \item Drews MS., Leonhardt A., Pirogova N., \textbf{Richter FG.}, […] Borst, A. (2020). Dynamic Signal Compression for Robust Motion Vision in Flies. \textit{Current Biology} 30, 209-221.
     
    \item \textbf{Richter FG.}, Fendl S., Haag J., Drews MS., Borst A. (2018). Glutamate Signaling in the Fly Visual System. \textit{iScience} 7, 85-95.
    
    \item Arenz A., Drews MS., \textbf{Richter FG.}, Ammer G., Borst A. (2017). The Temporal Tuning of the \textit{Drosophila} Motion Detectors Is Determined by the Dynamics of Their Input Elements. \textit{Current Biology} 27, 929-944.
    
    \item Martelli C., Pech U., […], \textbf{Richter FG}., Wegener C., Fiala A., Riemensperger T. (2017). SIFamide Translates Hunger Signals into Appetitive and Feeding Behavior in \textit{Drosophila}. \textit{Cell reports} 20, 464–478.
        
    
\end{itemize}